OptiFit project update

### 2021-03-10 docs/slides/2021-03-11_bistro.Rmd
Make xaringan theme work

---
title: "OptiFit project update"
subtitle: "+ a case study in debugging"
author: "Kelly Sovacool"
date: "2021-03-11 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    css: libs/xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      #titleSlideClass: ['center', 'middle', 'title-slide']
    chakra: libs/remark-latest.min.js
    self_contained: true
---

@@

# TODO: use http urls instead of here filepaths for figures
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_light(
  header_font_google = google_font("Helvetica"),
  text_font_google = google_font("Helvetica")
)
# style_mono_light(base_color = "#23395b")
# style_mono_accent(
#   base_color = "#1c5253",
#   header_font_google = google_font("Josefin Sans"),
#   text_font_google   = google_font("Montserrat", "300", "300i"),
#   code_font_google   = google_font("Fira Mono")
# )
```

@@

>>>>

---
title: "OptiFit project update"
subtitle: "+ a case study in debugging"
author: "Kelly Sovacool"
date: "2021-03-11 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      #titleSlideClass: ['center', 'middle', 'title-slide']
    chakra: libs/remark-latest.min.js
    self_contained: true
---

@@

```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#23395b",
  header_font_google = google_font("Helvetica"),
  text_font_google = google_font("Helvetica")
)
# style_mono_light(base_color = "#23395b")
# style_mono_accent(
#   base_color = "#1c5253",
#   header_font_google = google_font("Josefin Sans"),
#   text_font_google   = google_font("Montserrat", "300", "300i"),
#   code_font_google   = google_font("Fira Mono")
# )
```

@@

distance threshold: clumping vs splitting. some bacteria have multiple copies of rRNA gene.
